---
title: "R Bridge Week 2 Assignment"
author: "Donald Butler"
date: "7/30/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Select a random dataset

US Macroeconomic Data (1957–2005, Stock \& Watson)
  https://vincentarelbundock.github.io/Rdatasets/doc/AER/USMacroSW.html
  https://vincentarelbundock.github.io/Rdatasets/csv/AER/USMacroSW.csv

```{r load_data}
# github csv location
csvfile <- 'https://raw.githubusercontent.com/dab31415/SPS-Bridge-R/main/USMacroSW.csv'

df <- read.csv(csvfile)
```

## Exercise #1.

Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes.

```{r summary}
summary(df)

sprintf('3-month treasury bill: mean = %.3f; median = %.3f',mean(df$tbill),median(df$tbill))
sprintf('1-year treasury bond: mean = %.3f; median = %.3f',mean(df$tbond),median(df$tbond))

```

## Exercise #2.

Create a new data frame with a subset of the columns and rows. Make sure to rename it.

```{r subset}
# select the first 50 rows, with columns x, unemp, tbill, and tbond
my_df <- df[1:50,c(1:2,5:6)]
```

## Exercise #3.

Create new column names for the new data frame.

```{r column_names}
names(my_df) <- c('index','unemployement_rate','3-month tbill rate','1-year bond rate')
```

## Exercise #4.

Use the summary function to create an overview of your new data frame. Then print the mean and median for the same two attributes. Please compare.

```{r}
summary(my_df)

sprintf('3-month treasury bill: mean = %.3f; median = %.3f',mean(my_df$`3-month tbill rate`),median(my_df$`3-month tbill rate`))
sprintf('1-year treasury bond: mean = %.3f; median = %.3f',mean(my_df$`1-year bond rate`),median(my_df$`1-year bond rate`))
```
Interest rates for treasury bills and treasury bonds were lower in the first 50 quarters when compared with the original dataset.

## Exercise #5.

For at least 3 values in a column please rename so that every value in that column is renamed. For example, suppose I have 20 values of the letter “e” in one column. Rename those values so that all 20 would show as “excellent”.

```{r}
my_df$year <- 1957 + floor((my_df$index-1)/4)
my_df$qtr[(my_df$index-1) %% 4 == 0] <- 'First'
my_df$qtr[(my_df$index-1) %% 4 == 1] <- 'Second'
my_df$qtr[(my_df$index-1) %% 4 == 2] <- 'Third'
my_df$qtr[(my_df$index-1) %% 4 == 3] <- 'Fourth'

```

The dataset I selected wasn't conducive to completing this exercise as written. I used similar selection techniques to populate a new column for quarter. I played around with a datetime field, but wasn't having much luck.

## Exercise #6.

Display enough rows to see examples of all of steps 1-5 above.

```{r}
head(my_df,15)
```

